Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-03-13 Grassmannian_cells.tex
Fixed some typos in proof of Corollary 5.18

\begin{document}
\begin{abstract}
  We prove that all quiver Grassmannians for preprojective representations of a generalized Kronecker quiver admit a cell decomposition into affine spaces.  
  In the process, we introduce a class of regular representations which arise as quotients of consecutive preprojective representations.
  Cell decompositions for quiver Grassmannians of these ``truncated preprojectives'' are also established. 
  We also provide two natural combinatorial labelings for these cells.
  On the one hand, the cells are in bijection with compatible pairs in a maximal Dyck path as predicted by the theory of cluster algebras.
  On the other hand, they are labeled by certain subsets of a so-called $2$-quiver attached to a (truncated) preprojective representation.
  As there is a natural bijection between these two labelings this gives also a geometric explanation for the appearance of Dyck path combinatorics in the theory of quiver Grassmannians. 
\end{abstract}

>>>>

\begin{document}
\begin{abstract}
  We prove that all quiver Grassmannians for preprojective representations of a generalized Kronecker quiver admit a cell decomposition into affine spaces.  
  In the process, we introduce a class of regular representations which arise as quotients of consecutive preprojective representations.
  Cell decompositions for quiver Grassmannians of these ``truncated preprojectives'' are also established. 
  We also provide two natural combinatorial labelings for these cells.
  On the one hand, the cells are in bijection with compatible pairs in a maximal Dyck path as predicted by the theory of cluster algebras.
  On the other hand, they are labeled by certain subsets of a so-called $2$-quiver attached to a (truncated) preprojective representation.
  As there is a natural bijection between these two labelings, this also gives a geometric explanation for the appearance of Dyck path combinatorics in the theory of quiver Grassmannians. 
\end{abstract}
